\href{https://zenodo.org/badge/latestdoi/130237492}{\tt }

This is a template library for fast particle filtering. Templated abstract base classes for different particle filters are provided (e.\+g. the Bootstrap Filter, the Auxiliary Particle Filter, Rao-\/\+Blackwellized particle filter, etc.), as well as non-\/abstract (but indeed templated) base classes for closed form filtering algorithms (e.\+g. Kalman Filter, Hidden Markov Model filter, etc.).

Once you have a certain model in mind, all you have to do is make it into a class that inherits from the filter you want to use!

\subsection*{Installation}

This is a header-\/only library, so there is no building necessary. When you use it in another project, make sure to compile with C++11 enabled ({\ttfamily -\/std=c++11}), and to include the {\ttfamily include} directory of this project.

Note, also, that this code all makes use of \href{http://eigen.tuxfamily.org/}{\tt Eigen} and \href{https://www.boost.org/}{\tt Boost}.

\subsection*{Examples}

Don\textquotesingle{}t know how to use this? Check out the \href{https://github.com/tbrown122387/pf/tree/master/examples}{\tt {\ttfamily examples}} directory! Check {\ttfamily pf/examples/\+Makefile} to make sure it jives with your directories, and then run {\ttfamily make}. After that, run {\ttfamily ./examples ./data/svol\+\_\+y\+\_\+data.csv} and you\textquotesingle{}ll see the filtering output from {\ttfamily examples/svol\+\_\+comparison.\+cpp}.

\subsection*{Citation}

Click the \char`\"{}\+D\+O\+I\char`\"{} link above. Or, if you\textquotesingle{}re impatient, click \href{https://zenodo.org/record/2633289/export/hx}{\tt \textquotesingle{}here\textquotesingle{}} for a Bibtex citation. 